---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geojp

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/527063683.svg)](https://zenodo.org/doi/10.5281/zenodo.10205233)
<!-- badges: end -->

The goal of geojp is to provide an easy access to various geographical data of Japan.

## Installation

You can install the development version of geojp from [GitHub](https://github.com/) with:

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("babayoshihiko/geojp")
```

Load (attach) package **geojp**.

```{r setup}
library(geojp)
```

## Census

Load census boundary information. Specify the prefecture code (code_pref) and municipality code (code_muni). Here is an example for Osaki City (215) in Miyagi Prefecture (4).

```{r echo=T, eval=F}
sfCensus <- geojp::read_census_tract(code_pref = 4, code_muni = 215)
head(sfCensus)
```

```{r echo=F, eval=T}
sfCensus <- geojp::read_census_tract(code_pref = 4, code_muni = 215, data_dir = "~/Download/data.noindex")
head(sfCensus)
```

The census has many columns, so only the important ones have been cut out.

Ordinance-designated cities will be in units of administrative districts. The `read_census_odcity()` function returns all the wards with the name of the ordinance-designated city.

```{r echo=T, eval=F}
sfCensus2 <- geojp::read_census_odcity("京都市")
head(sfCensus2)
```

```{r echo=F, eval=T}
sfCensus2 <- geojp::read_census_odcity("京都市", data_dir = "~/Downloads/data.noindex")
head(sfCensus2)
```

Additional attribute information is set. Attributes are obtained using the `attr()` function. One particularly important attribute is the source. The source can be retrieved as follows

```{r}
attr(sfCensus2, "sourceName")
attr(sfCensus2, "sourceURL")
```

## National Land Information

Load the zoning information from the National Land Information. Specify the prefecture code (code_pref) and municipality code (code_muni). The 2011 and 2019 versions are available, so we will try the 2011 version this time.

For more information about the National Land Information, see [National Land Information Download Service](https://nlftp.mlit.go.jp/ksj/index.html).

The return value is an `sf` object.

```{r  echo=T, eval=F}
sfYouto <- geojp::read_landnuminfo_landuse(code_pref = 26, code_muni = 100, year = 2011)
```

```{r  echo=F, eval=T}
sfYouto <- geojp::read_landnuminfo_landuse(code_pref = 26, code_muni = 100, year = 2011, data_dir = "~/Download/data.noindex")
```

The `A29_004` and `A29_005` columns, which indicate the zoning class, are of type factor.

```{r}
levels(sfYouto$A29_005)
```

Additional attribute information is set. Attributes are obtained using the `attr()` function. One particularly important attribute is the source. The source can be retrieved as follows

```{r}
attr(sfYouto, "sourceName")
attr(sfYouto, "sourceURL")
```

The attribute "col" is the column name used for color separation. The attribute "palette" is the color palette for color separation. This is matched as closely as possible to the colors of the intended use area according to the Japanese Industrial Standards (JIS).

```{r}
attr(sfYouto, "palette")
```

## tmap

Use package **tmap** to display the usage area. The last font specification is required only for macOS.

```{r}
library(tmap)
# Create a map.
myTm <- tm_shape(sfYouto) +
          tm_polygons(col = attr(sfYouto, "col"), palette = attr(sfYouto, "palette"), alpha = 0.8) + 
           tm_borders()
myTm <- myTm +
      tm_scale_bar() +
      tm_layout(title = "京都市",
                legend.outside = FALSE, 
                fontfamily = "HiraginoSans-W3")
```

Display the plot.

```{r}
myTm
```

To save, use the `tmap_save()` function.

```{r eval = FALSE}
tmap_save(tm = myTm, filename = "map.png")
```

You can also superimpose census and zoning maps.

In addition, you can use The Geospatial Information Authority of Japan standard map in tiled format as a base map.

https://maps.gsi.go.jp/development/ichiran.html

```{r}
library(tmap)
tmap_mode("view")
# Create a map.
myTm <- tm_shape(sfCensus2) +
          tm_polygons("JINKO", alpha = 0.8) 
myTm <- myTm +
          tm_shape(sfYouto) +
          tm_polygons(col = attr(sfYouto, "col"), palette = attr(sfYouto, "palette"), alpha = 0.8) + 
           tm_borders()
myTm <- myTm +
      tm_basemap(server = "https://cyberjapandata.gsi.go.jp/xyz/std/{z}/{x}/{y}.png")
myTm <- myTm +
      tm_scale_bar() +
      tm_layout(title = "京都市",
                legend.outside = FALSE, 
                fontfamily = "HiraginoSans-W3")
myTm
```

## mapview

```{r}
library(mapview)
mapviewOptions(fgb = FALSE) # needed when creating web pages
mapview(sfYouto[attr(sfYouto, "col")], col.regions = attr(sfYouto, "palette"), fgb = FALSE)
```
