---
title: "Introducing geojp"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{geojp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tmap)
library(mapview)
library(leaflegend) # for tmap v4
```

## Installation and load

This is only necessary at the beginning. However, as it is still under development, it is advisable to repeat it regularly.

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("babayoshihiko/geojp")
```

Load (attach) the package **geojp**.

```{r setup}
library(geojp)
```

## Census

Load the census boundary information. Specify the prefecture code (code_pref) and the municipality code (code_muni). Example for Osaki City (215) in Miyagi Prefecture (4).

```{r, echo = T, eval = F}
sfCensus <- geojp::read_census_tract(code_pref = 4, code_muni = 215)
head(sfCensus)
```
```{r, echo = F, eval = T}
sfCensus <- geojp::read_census_tract(code_pref = 4, code_muni = 215, data_dir = "~/data.noindex/Census")
head(sfCensus)
```

The census has a large number of columns, so only the important ones have been cut out.

Ordinance-designated cities are in units of administrative wards. The `read_census_odcity` function returns all wards with the name of the ordinance city.

```{r, echo = T, eval = F}
sfCensus2 <- geojp::read_census_odcity("京都市")
head(sfCensus2)
```
```{r, echo = F, eval = T}
sfCensus2 <- geojp::read_census_odcity("京都市", data_dir = "~/data.noindex/Census")
head(sfCensus2)
```

Additional attribute information is set. Attributes are obtained using the `attr()` function. One particularly important attribute is the source. Sources can be retrieved as follows.

```{r}
attr(sfCensus2, "sourceName")
attr(sfCensus2, "sourceURL")
```

## Land Numerical Information

Load the zoning of the National Land Numeric Data. Specify the prefecture code (code_pref) and municipality code (code_muni). The 2011 (Heisei 23) and 2019 (2019) editions are available, so we will try the 2011 edition this time.

For more information on the National Geodetic Information, see [National Land Numerical Information Download Service](https://nlftp.mlit.go.jp/ksj/index.html).

The return value is an `sf` object.

```{r, echo = T, eval = F}
sfYouto <- geojp::read_landnuminfo_landuse(code_pref = 26, 100)
```
```{r, echo = F, eval = T}
sfYouto <- geojp::read_landnuminfo_landuse(code_pref = 26, 100, data_dir = "~/data.noindex/A29")
```

Columns `A29_004` and `A29_005`, which indicate the zoning class, are of type factor.

```{r}
levels(sfYouto$A29_005)
```

Additional attribute information is set. Attributes are obtained using the `attr()` function. One particularly important attribute is the source. Sources can be retrieved as follows.

```{r}
attr(sfYouto, "sourceName")
attr(sfYouto, "sourceURL")
```

Attribute "col" is the column name used for colour coding. Attribute "palette" is the colour palette for colour coding. This is matched as far as possible to the colours of the application area according to the Japanese Industrial Standards (JIS).

```{r}
attr(sfYouto, "palette")
```

## tmap

You can use the package **tmap** to display the intended use area. The last font specification is only required for macOS.

```{r}
library(tmap)
# Create a map with tmap (v4).
myTm <- tm_shape(sfYouto) +
      tm_polygons(fill = attr(sfYouto, "col"), 
              palette = attr(sfYouto, "palette"), 
              alpha = 0.8) + 
      tm_borders()
myTm <- myTm +
      tm_scalebar() +
      tm_layout(tm_title = "京都市",
              legend.outside = FALSE, 
              legend.text.fontfamily = "HiraginoSans-W3")
```

For reference purpose, the below uses tmap(v3).

```{r eval = FALSE}
library(tmap)
# Create a map with tmap (v3).
myTm <- tm_shape(sfYouto) +
          tm_polygons(col = attr(sfYouto, "col"), palette = attr(sfYouto, "palette"), alpha = 0.8) + 
           tm_borders()
myTm <- myTm +
      tm_scale_bar() +
      tm_layout(title = "京都市",
                legend.outside = FALSE, 
                fontfamily = "HiraginoSans-W3")
```

Display the plot.

```{r}
myTm
```

You can save with the `tmap_save()` function.

```{r eval = FALSE}
tmap_save(tm = myTm, filename = "map.png")
```

It is also possible to overlay census and zoning maps.

In addition, you can use Geospatial Information Authority of Japan's standard maps in tiled format as a base map.

```{r}
library(tmap)
tmap_mode("view")

base_map = geojp::get_tile_server()

# Create a map with tmap (v4).
myTm <- tm_shape(sfCensus2) +
          tm_polygons("JINKO", alpha = 0.8) 
myTm <- myTm +
          tm_shape(sfYouto) +
          tm_polygons(fill = attr(sfYouto, "col"), 
                      palette = attr(sfYouto, "palette"), alpha = 0.8) + 
          tm_borders()
myTm <- myTm +
      tm_basemap(server = base_map$server)
myTm <- myTm +
      tm_scalebar() +
      tm_layout(tm_title = "京都市",
                legend.outside = FALSE, 
                legend.text.fontfamily = "HiraginoSans-W3")
myTm
```

Source: `r base_map$reference`

## mapview

```{r}
library(mapview)
mapviewOptions(fgb = FALSE) # needed when creating web pages
mapview(sfYouto[attr(sfYouto, "col")], col.regions = attr(sfYouto, "palette"), fgb = FALSE)
```
